\documentclass[a4paper]{article}
\usepackage[a4paper, total={6in, 8in}, margin=0.5in]{geometry}
\usepackage{marvosym}
\usepackage{fontspec}
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
%\begin{comment}
%\end{comment}
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{hyperref}
\usepackage{lipsum}
%\usepackage{twemojis}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
\hyphenation{im-pre-se}
\usepackage[absolute]{textpos}
\usepackage{amssymb}
\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}




\begin{document}
\pagestyle{empty} 						% non-numbered pages
\font\fb=''[cmr10]'' 						%for use with \LaTeX command

%--------------------TITLE-------------
\par	{\centering
	ॐ																																\\
	\href{https://contacttheteam.github.io/LivingSpace/}{$ \Uparrow$}{sagarPanchal}																																\\
	\small \href{mailto:sagarp.creator@gmail.com}{sagarp.creator@gmail.com}		\textbullet{+1 (279) 842-6274}		\textbullet {Folsom, CA - 95630}																		\\
	\small \href{https://www.linkedin.com/in/sagar-panchal-55b435122/}{https://www.linkedin.com/in/sagar-panchal-55b435122/}		\textbullet \href{https://contacttheteam.github.io/LivingSpace/}{https://contacttheteam.github.io/LivingSpace/}		\par}
	
%Section: About--------------------------------------
\section	{	About		}
	\begin{tabular}{ll}
		\textsc{	Engineer with experience in Computers,  Machines \& Automation.					}\\
		\textsc{	Looking forward,  towards a role that offers better Individual and Professional growth.	}
	\\\end{tabular}



%Section: Education--------------------------------------
\section	{	Education		}
	\begin{tabular}{rl}
		\small{}\textsc{		Jan 2016-17	} 		& 		\textsc{	MS, Electrical \& Computer engineering, 		\small {(3.41/4)}			}	\\
 											& 		\textsc{	Polytechnic institute of technology, NYU							}	\\
 		\small{}\textsc{		Jun 2010-14	} 		& 		\textsc{	BE, Instrumentation \small{\&} Controls,		\small {(7.04/10)}		}	\\
 											& 		\textsc{	Svit, GTU													}	\\
	\end{tabular}

%Section: Technical Skills--------------------------------------
\section{		Skills																													}
	\begin{tabular}{rl}	\small{}
	 	\small{}\textsc{		Computer Programming:	}	& \textsc{					java(primary), \small{c/c\texttt{++} (secondary)}, \LaTeX (tirtiary), git,			}	\\
  												& \textsc{					web(html, css, js), desktop(javaFx, awt)							} 	\\
 		\small{}\textsc{		Automation:			}	& \textsc{					micro-controllers \& single board computers,						}	\\
  												& \textsc{					PLCs(ladder-logic, FBD), hmi/scada								} 	\\
 		\small{}\textsc{		Industries served:		}	& \textsc{					machineries, manufacturing, control panels, solar energy,				}	\\
  												& \textsc{					Education													} 	\\
	\end{tabular}

%Section: Work--------------------------------------
\section	{	Work Experience																										}
%
\textbf	{	$\square$ Automation Engineer																						} \hfill \emph {Jan 22 - present	}	\\
\textsc	{	nor-cal controls, california																											}	\\
%
\textbf	{	$\square$ Software Engineer - Machine Automation																		} \hfill \emph {Feb 18 - Nov 21	}	\\
\textsc	{	mini-circuits, ny																													}	\\
\textbullet	{	Primarily responsible for development and maintenance of Software for Robotics and Computer Vision Projects.										}	\\
\textbullet	{	Upgrading legacy Control Programs and rewrite them using new technology (mostly Java).														}	\\
\textbullet	{	Troubleshooting machine/automation/software issues related to production.																	}	\\
\textbullet	{	Development and maintenance of the Website: \href{https://www.minicircuits.com/}{https://www.minicircuits.com/}										}	\\
\textbullet	{	Development and maintenance of Web/Desktop Applications to support Database Maintenance.													}	\\
\textbullet	{	\textbf{Universal Rotary Machine}:																									}	\\
\textbullet	{	Integrated capabilities from different Machines into one to include more range of products to be tested.												}	\\
\textbullet	{	Successfully implemented Visual Inspection on the machine before packing the units.															}	\\
\textbullet	{	\textbf{Laser Measurement System for Mechanical Switches}:																				}	\\
\textbullet	{	An R\&D Project to verify dimensions of Various Switch bodies using a Laser Displacement Sensor.													}	\\
\textbullet	{	Documenting project status on Agile tool (JIRA).																						}	\\
%
\textbf	{	$\square$ Developer Intern																						} \hfill \emph {Sep - Dec 17	}	\\
\textsc	{	revmax fleet optimization, ny																										}	\\
\textbullet	{	Developing Firmware for SidewalkIQ Sensor using Doppler Radar to monitor sidewalk activities.													}	\\
\textbullet	{	Successfully deployed sensors at various NYC locations.																					}	\\
\textbullet	{	R\&D to improve data consistency and efficiency of data storage/transfer to Server for further processing.												}	\\
%
\textbf	{	$\square$ Instructor (ITEST Program)																				} \hfill \emph {May - Aug 17	}	\\
\textsc	{	robotics \& mechatronics dpt., NYU																									}	\\
\textbullet	{	Mentor to Robotics Club Programming Team for Robotics competitions (First Robotics \& Vex Robotics).												}	\\
\textbullet	{	Teaching concepts of Computer Programming to Robotics Club Team.																		}	\\
%
\textbf	{	$\square$ Lead Instructor (CREST Program)																			} \hfill \emph {Feb 18 - Nov 21	}	\\
\textsc	{	center for k12 stem education, NYU																									}	\\
\textbullet	{	Training High School Interns with Computer Programming (Arduino C), IoT, Robotics \& 3D-Printing activities.											}	\\
\textbullet	{	\textbf{Autonomous Car (Mouse in a Maze)} - STM32 Board: \href{https://github.com/sap586/RTES_Project}{https://github.com/sap586/RTES\_Project}			}	\\
\textbullet	{	\textbf{Wireless Robot Controller} - Arduino: \href{https://github.com/sap586/WirelessRobotDay5Activity}{https://github.com/sap586/WirelessRobotDay5Activity}	}	\\
%
\textbf	{	$\square$ Design Engineer																						} \hfill \emph {Jun 14 - Jan 16	}	\\
\textsc	{	prima automation, IN																												}	\\
\textbullet	{	Embedded Software Development on PLCs, micro-controllers \& Report Generation.																}	\\
\textbullet	{	Front-end (UX) design on HMI/SCADA for Industrial Automation applications.																	}	\\
\textbullet	{	Troubleshooting and upgrading legacy Automation projects (mostly on Siemens Systems).														}	\\
\textbullet	{	Electrical \& Control Panel Layout for Industrial Automation and Robotics (E-plan, AutoCAD).														}	\\
%
 \textbf	{	$\square$ Trainee Engineer																						} \hfill \emph {Aug 13 - May 14	}	\\
\textsc	{	neoplast (I) pvt. ltd., IN																											}	\\
\textbullet	{	Embedded Software Development on Siemens PLC and Front-end (UX) Design on SCADA.														}	\\
%
\hrule
\small 	{	\hfill {This document is prepared using \LaTeX. Click \href{https://raw.githubusercontent.com/contacttheteam/LivingSpace/master/LaTeX/sagar.creator.tex}{here} to download the source code.}																	}\\	

\end{document}